### 2018-10-22 pkg/model4you/inst/JORS/man_model4you.Rnw
nice header
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1843 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 57dc10457bec608c981aa10c7dd792a152d7425f
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2174 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: b7e23f0d093fd036a6f75a8abcfc0edb5815a2b2
update manuals
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2352 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0f27fc1e71b261c31a167c24228d74a278b7a34c

@@

To complete this template, please replace the blue text with your own. The paper has three main sections: (1) Overview; (2) Availability; (3) Reuse potential. \\

Please submit the completed paper to: editor.jors@ubiquitypress.com

@@

\section*{Abstract}
Typical models estimating treatment effects assume that the treatment effect is
the same for all individuals.  Model-based recursive partitioning allows to
relax this assumption and to estimate stratified treatment effects (model-based
trees) or even personalised treatment effects (model-based forests).  With
model-based trees one can compute treatment effects for different strata of
individuals. The strata are found in a data driven fashion and depend on
characteristics of the individuals.  Model-based random forests allow for a
similarity estimation between individuals in terms of model parameters (e.g.\
intercept and treatment effect). The similarity measure can then be used to
estimate personalised models.  The R package \emph{model4you} implements these
stratified and personalised models with a focus on ease of use and
interpretability so that clinicians and other users can take the model they
usually use for the estimation of the average treatment effect and with a few
lines of code get a visualisation that is easy to understand and interpret.

@@

@@

\section*{Implementation and architecture}
The R package \emph{model4you} is focused on ease of use and interpretability.
Users can take a simple model that they know and understand as basis and simply
plug it into \Sexpr{'pmtree()'} or \Sexpr{'pmforest()'} depending on whether
they want subgroup wise or personalised models. The basis for these
functionalities is provided by the \emph{partykit} 
package which is a widely
used R package for trees and forests \citep{hothorn_partykit_2015, hothorn_partykit_2017}. 
The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities to allow for the computation of personalised models and to 
improve usability and interpretability.

>>>>

%% revised text
\newcommand{\new}[1]{{\color{blue} #1}}

@@

%To complete this template, please replace the blue text with your own. The paper has three main sections: (1) Overview; (2) Availability; (3) Reuse potential. \\

%Please submit the completed paper to: editor.jors@ubiquitypress.com

@@

\section*{Abstract}
Typical models estimating treatment effects assume that the treatment effect is
the same for all individuals.  Model-based recursive partitioning allows to
relax this assumption and to estimate stratified treatment effects (model-based
trees) or even personalised treatment effects (model-based forests).  With
model-based trees one can compute treatment effects for different strata of
individuals. The strata are found in a data driven fashion and depend on
characteristics of the individuals.  Model-based random forests allow for a
similarity estimation between individuals in terms of model parameters (e.g.\
intercept and treatment effect). The similarity measure can then be used to
estimate personalised models.  The R package \emph{model4you} implements these
stratified and personalised models \new{in the setting with two randomly
assigned treatments} with a focus on ease of use and
interpretability so that clinicians and other users can take the model they
usually use for the estimation of the average treatment effect and with a few
lines of code get a visualisation that is easy to understand and interpret.

@@

Currently the R package \emph{model4you} can handle only

@@

\section*{Implementation and architecture}
The R package \emph{model4you} is focused on ease of use and interpretability.
Users can take a simple model that they know and understand as basis.
\new{
Models currently available for use are linear models (function \Sexpr{'lm()'}
in R), generalised
linear models (\Sexpr{'glm()'}) and survival models (\Sexpr{'survreg()'} and
\Sexpr{'coxph()'} from the R package \emph{survival}). Models are restricted
to those with a single binary covariate (e.g. two treatment options).
The user can simply plug the model object into \Sexpr{'pmtree()'} or
\Sexpr{'pmforest()'} depending on whether they want subgroup wise or
personalised models.
}

The basis for these
functionalities is provided by the \emph{partykit}
package which is a widely
used R package for trees and forests \citep{hothorn_partykit_2015, hothorn_partykit_2017}.
The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities to allow for the computation of personalised models and to
improve usability and interpretability.
